Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-18 article.tex
add parameters for GTE and GENIE3

% Explaining the method (thèse de Gilles)
% Genie3 : better in auprc while worse in auroc than GTE. Why?
% Genie3 : "Conditioning" better and better but need a lot of trees
% Correlation : Already give good results

% Partial correlation : Obvious improvements (both metric) because of the conditioning

@@

GTE is a method which characterizes a relationship between neurons by an
estimation of the generalized transfer entropy \citep{stetter2012model}. The
goal of this method tries to see if the next time step value is better from
the previous values of this time series or from time series of other neurons.

GENIE3 is a tree-based method which sees the network inference problem as $p$,
the number of variables, independent supervised learning problems (todo cite:
Irrthum?Van Anh?Pierre?). Formally, each sub-problem consists in the
prediction of one variable, the target, from the remaining $p-1$ variables.
This method uses random forests to estimate the target variable and variable
importances can be derived to estimate the adjacency matrix $A$ (see (todo
cite) for a more detailed description of the inference method).

@@

%% Depth -- Gilles chapitre 7

@@

Interestingly, an easy way to improve results for asymmetric method (see
Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered
network. It proves once again that trying to detect the link direction is more
penalizing than rewarding.

>>>>

% Explaining the method (thèse de Gilles)

@@

\textcolor{red}{à vérifier} GTE is a method which characterizes a relationship
between neurons by an estimation of the generalized transfer entropy
\citep{stetter2012model}. The goal of this method tries to see if the next
time step value is better from the previous values of this time series or from
time series of other neurons. In Tab.\ref{tab:tab1}, default parameters were
used to infer networks.

GENIE3 is a tree-based method which sees the network inference problem as $p$,
the number of variables, independent supervised learning problems (todo cite:
Irrthum?Van Anh?Pierre?). Formally, each sub-problem consists in the
prediction of one variable, the target, from the remaining $p-1$ variables.
This method uses random forests to estimate the target variable and variable
importances can be derived to estimate the adjacency matrix $A$ (see (todo
cite) for a more detailed description of the inference method). We compute
$10000$ trees for each subproblem with the randomization parameter equals to
$\log_2{p}$ and we limite the tree max-depth to respectively $1$, $2$ and $3$.

% Partial correlation : Obvious improvements (both metric) because of the conditioning
% Correlation : Already give good results

@@

%% Depth -- Gilles chapitre 7
% Genie3 : better in auprc while worse in auroc than GTE. Why?
% Genie3 : "Conditioning" better and better but need a lot of trees

@@

Interestingly, an easy way to improve results for asymmetric methods (see
Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered
network. It proves once again that trying to detect the link direction is more
penalizing than rewarding.
